BFS search in miniKanren

### 2019-03-15 Paper/paper.tex
tuning

The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
The order of the answers reflects the order miniKanren discovers them:
the leftmost answer is the first one. This result is not suprising:
to generate the first answer, \texttt{'()}, miniKanren needs to apply
\texttt{repeato} only once and the later answers need more recursive
applications. In this example, the cost of each answer is the same as
one more than the number of \texttt{*}s: the cost of \texttt{'()} is 1,
the cost of \texttt{'(*)} is 2, and so on.

@@

The results are not cost-respecting. For example, \texttt{'(a a)} occurs before
\texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
The problem is that iDFS strategy prioritizes the first \texttt{conde} case
considerablely. In general, when every conde case are equally productive, the iDFS
strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
which share the same portion as the second last one.

>>>>

The above \texttt{run} generates 4 answers. All are lists of \texttt{*}s.
The order of the answers reflects the order miniKanren discovers them:
the first answer in the list is first discovered. This result is not suprising:
to generate the first answer, \texttt{'()}, miniKanren needs to apply
\texttt{repeato} only once and the later answers need more recursive
applications. In this example, the cost of each answer is the same as
one more than the number of \texttt{*}s: the cost of \texttt{'()} is 1,
the cost of \texttt{'(*)} is 2, and so on.

@@

The results are not cost-respecting. For example, \texttt{'(a a)} occurs before
\texttt{'(b)} while \texttt{'(a a)} is associated with a higher cost. 
iDFS strategy is the cause, since it prioritizes the first \texttt{conde} case
considerablely. When every conde case are equally productive, the iDFS
strategy takes $1/2^{i}$ answers from the $i$-th case, except the last case,
which share the same portion as the second last one.
